---
title: "Annotation of Predicted ORFs"
output:
  html_document:
    keep_md: true
---

Unfortunately, we do use a licensed version of KEGG and USEARCH for large searches and I can not share those, but the outputs from the search are available at in the intermediate_results directory of the github repo. We prefer ublast from USEARCH (here version 7.0.10) to do our large scale blasting and the free version of USEARCH would not work to configure the ublast database of KEGG. Here, we will be doing protein-protein searches.  First, we need to configure the usearch datbase from the KEGG sequeneces:

```{r, engine='bash'}
./usearch7.0.10 -makeudb_ublast keggV69.genes.pep.txt -output keggV69.genes.pep.udb
```

I included the exact version of PHAST prophage and viral database used in the original search (April 15, 2015). You can download the latest version though using: wget http://phast.wishartlab.com/phage_finder/DB/prophage_virus.db
	
I like to replace all spaces in PHAST database with underscores so usearch outputs the whole entry in the output file. Did so manually in a text editor.

Create the userach database for PHAST:

```{r, engine='bash'}
./usearch7.0.10 -makeudb_ublast prophage_virus.db -output prophage_virus.udb
```

Search Viral against KEGG:

```{r, engine='bash'}
./usearch7.0.10 -ublast vmg.orfs_aa.filter.fasta -db keggV69.genes.pep.udb -evalue 1e-5 -blast6out vmg.ublast.kegg.txt -strand both -top_hits_only -threads 15
```

Search Viral against PHAST:

```{r, engine='bash'}
./usearch7.0.10 -ublast vmg.orfs_aa.filter.fasta -db prophage_virus.udb -evalue 1e-5 -blast6out vmg.ublast.phast.txt -strand both -top_hits_only -threads 15
```

Search Total against KEGG:

```{r, engine='bash'}
./usearch7.0.10 -ublast bmg.orfs_aa.filter.fasta -db keggV69.genes.pep.udb -evalue 1e-5 -blast6out bmg.ublast.kegg.txt -strand both -top_hits_only -threads 15
```

Search Total against PHAST:
	
```{r, engine='bash'}
./usearch7.0.10 -ublast bmg.orfs_aa.filter.fasta -db prophage_virus.udb -evalue 1e-5 -blast6out bmg.ublast.phast.txt -strand both -top_hits_only -threads 15
```

Search Illumina Viral against KEGG:

```{r, engine='bash'}
./usearch7.0.10 -ublast vmg.illumina.orfs_aa.filter.fasta -db keggV69.genes.pep.udb -evalue 1e-5 -blast6out vmg.illumina.ublast.kegg.txt -strand both -top_hits_only -threads 15
```

Search Illumina Viral against PHAST:
	
```{r, engine='bash'}
./usearch7.0.10 -ublast vmg.illumina.orfs_aa.filter.fasta -db prophage_virus.udb -evalue 1e-5 -blast6out vmg.illumina.ublast.phast.txt -strand both -top_hits_only -threads 15
```


