---
title: "Viral Beta Diversity"
output:
  html_document:
    keep_md: true
---

Two methods - median k-mer counts and distribution of ORFs among samples.

## Median K-mer Count

Use khmer software to compare k-mer profiles of different metagenomes. Load all viral metagenomes into counting first.

```{r, engine='bash', results='hide'}
mkdir viral_beta_div
for f in viral_qc/*finalQC.fastq
do
  filename=$(basename "$f")
  filename="${filename%_*}"
  load-into-counting.py -k 20 -N 4 -x 8e9 --report-total-kmers -s tsv viral_beta_div/"$filename""_k20.kh" $f
done
```

The script below is from https://github.com/qingpeng/igs-diversity/blob/master/scripts/get_comb_multi_old_median_kmer.py and I have provided the version of the script used in this analysis. Finds the median k-mer abundance across samples.

```{r, engine='bash', results='hide'}
cd viral_beta_div/
ls *k20.kh | awk '{ ORS=" "; print; }' > config.txt
printf "\n" >> config.txt
ls *finalQC.fastq | awk '{ ORS=" "; print; }' >> config.txt
printf "\n" >> config.txt
printf "55000000" >> config.txt
	
python ../scripts/get_comb_multi_old_median_kmer.py config.txt

cd ..
```

Remove reads that are not shared with at least one other sample. This helps to alleviate differences diven by sequencing errors. Sequencing errors generate new/false k-mers. The median k-mer counts are then normalized based on library size and the resulting normalized files are converted to biom format.

```{r, engine='bash', results='hide'}
perl scripts/khmer_multi_threshold.pl -khmer_multi_dir=viral_beta_div -threshold=1

mv *.comb.keep.txt viral_beta_div

cat viral_beta_div/*.comb.keep.txt > viral_beta_div/VMG.cat.comb.keep.txt

awk '{print $1,$2/629489,$3/2712098,$4/470915,$5/920397,$6/593047,$7/328660,$8/593530,$9/100696,$10/1350530,$11/1881525,$12/2138335,$13/276069,$14/499466,$15/526337,$16/703720}' viral_beta_div/VMG.cat.comb.keep.txt > viral_beta_div/VMG.cat.comb.keep.norm.txt

printf "ID VMG.10 VMG.11 VMG.12 VMG.13 VMG.14 VMG.15 VMG.1 VMG.2 VMG.3 VMG.4 VMG.5 VMG.6 VMG.7 VMG.8 VMG.9\n" > viral_beta_div/VMG.read_table.txt

cat viral_beta_div/VMG.cat.comb.keep.norm.txt >> viral_beta_div/VMG.read_table.txt

tr ' ' \\t < viral_beta_div/VMG.read_table.txt > viral_beta_div/VMG.read_table.tab.txt

biom convert -i viral_beta_div/VMG.read_table.tab.txt -o viral_beta_div/VMG.read_table.tab.biom --table-type="OTU table" --to-json
```

Calcualte the Bray-Curtis dissimilarity between samples based on the normalized median k-mer abundance and use the dissimilarities to construct an NMDS plot.

```{r, engine='bash', results='hide'}
beta_diversity.py -i viral_beta_div/VMG.read_table.tab.biom -o viral_beta_div/VMG.read_table_bc -m bray_curtis

nmds.py -i viral_beta_div/VMG.read_table_bc/bray_curtis_VMG.read_table.tab.txt -o viral_beta_div/VMG.read_table_bc_nmds.txt
```

```{r}
library(ggplot2)
library(vegan)
viral_bc <- read.table("viral_beta_div/VMG.read_table_bc/bray_curtis_VMG.read_table.tab.txt", header=TRUE, row.names=1)
viral_bc_matrix <- as.matrix(viral_bc)
viral_bc_dist <- as.dist(viral_bc_matrix)
	
viral_map <- read.table("viral_mapping.txt", sep="\t", header=TRUE)
viral_map$Animal <- as.factor(viral_map$Animal)
```

```{r}
multiplot <- function(..., plotlist = NULL, file, cols = 1, layout = NULL) {
  library(grid)
  plots <- c(list(...), plotlist)
  numPlots = length(plots)
  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)), ncol = cols, nrow = ceiling(numPlots/cols))
  }
    
	if (numPlots == 1) {
	  print(plots[[1]])
  } else {
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    for (i in 1:numPlots) {
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row, layout.pos.col = matchidx$col))
    }
  }
}

viral_nmds <- read.table("viral_beta_div/VMG.read_table_bc_nmds.txt", nrow = 15, sep = "\t", header=TRUE)
colnames(viral_nmds)[1] <- "ID"
viral_nmds_map <- merge(viral_nmds, viral_map, by = "ID")
names(viral_nmds_map)[5] <- "Steer"

shape_diet <- c("Corn" = 15, "27CDS" = 16, "55CS" = 17, "40MDGS" = 18)
shape_animal <- c("346" = 15, "259" = 16, "3244" = 17, "222" = 18, "3257" = 8)

viral_diet_nmds <- ggplot(viral_nmds_map, aes(NMDS1, NMDS2)) + geom_point(aes(color = Diet), size=2.5) +
  xlab("NMDS1") + ylab("NMDS2") + 
  guides(size = FALSE) + scale_shape_manual(name = "", values = shape_diet) + 
  labs(fill = "") +
  theme(legend.key = element_blank())
    
viral_animal_nmds <- ggplot(viral_nmds_map, aes(NMDS1, NMDS2)) + geom_point(aes(color = Steer), size=2.5) +
  xlab("NMDS1") + ylab("NMDS2") + 
  guides(size = FALSE) + scale_shape_manual(name = "", values = shape_animal) + 
  labs(fill = "") +
  theme(legend.key = element_blank())
    
tiff("figure_2b.tiff", height = 6, width = 12, units='in', res=600)
multiplot(viral_diet_nmds, viral_animal_nmds, cols = 2)
dev.off()
```

Use PERMANOVA tests to investigate statisticial differences based on diet and animal the sample was collected from. Additionally, PERMANOVA can be used on continous data - so broke down the diets into their main components and tested which component had a signifincant impact on viral community structure.

```{r}
adonis(viral_bc_dist ~ Diet + Animal, permutations=999, random=Animal, data=viral_map)

anova(betadisper(viral_bc_dist,viral_map$Diet))

anova(betadisper(viral_bc_dist,viral_map$Animal))

permutest(betadisper(viral_bc_dist,viral_map$Diet))

permutest(betadisper(viral_bc_dist,viral_map$Animal))
```

Also used dbRDA, adonis, and subsequent ordination plots to investigate influence of environmental factors (i.e. dietary components) on viral communities.

```{r}
library(data.table)
library(ggvegan)
library(grid)

map2 <- viral_map[c("pH", "Protein", "NDF", "K", "Zn", "VFA", "TDN", "ADF", "RFV", "Ca", "Cu", "Fe", "P", "Mg", "Mn", "S", "Na", "Mo")]
cor(map2)

viral_tab <- fread("viral_beta_div/VMG.read_table.tab.txt", header=TRUE, sep="\t")
viral_df <- as.data.frame(viral_tab)
row.names(viral_df) <- viral_df$ID
viral_df <- subset(viral_df, select=-c(ID))
viral_df_t <- t(viral_df)

viral_cap <- capscale(viral_df_t ~ TDN + Zn + Protein, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)
#save(viral_cap, file="viral_cap_read.RData")
#load("viral_cap_read.RData")


viral_cap <- capscale(viral_df_t ~ TDN + Protein + Zn, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Protein + Zn + TDN, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Protein + TDN + Zn, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Zn + TDN + Protein, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Zn + Protein + TDN, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

adonis(viral_bc_dist ~ TDN + Zn + Protein ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ TDN + Protein + Zn ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Protein + Zn + TDN ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Protein + TDN + Zn ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Zn + TDN + Protein ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Zn + Protein + TDN ,  permutations=999, data=viral_map)

viral_cap <- capscale(viral_df_t ~ TDN + Zn + Protein, data = viral_map, distance = "bray")
test <- fortify(viral_cap)
site_df <- subset(test, test$Score == "sites")
site_df2 <- data.frame(diet= c("27CDS","55CS","55CS","27CDS","Corn","40MDGS","Corn","Corn","40MDGS","27CDS","55CS","40MDGS","40MDGS","Corn","55CS"), site_df)
biplot_df <- subset(test, test$Score == "biplot")
biplot_df2 <- data.frame(text_x = as.numeric(c("0.82", "-0.30", "-0.25")), biplot_df)
biplot_df3 <- data.frame(text_y = as.numeric(c("0.33", "-0.95", "-0.30")), biplot_df2)
biplot_df3$Label[3] = "Pro"

tiff("figure_4b.tiff", width = 6, height = 6, units = 'in', res = 300)
ggplot(data = site_df2, aes(Dim1, Dim2)) + 
    geom_point(aes(color = diet)) +
  	geom_segment(data=biplot_df3,aes(x=0,xend=Dim1,y=0,yend=Dim2), arrow = arrow(type="closed",length = unit(0.2, "cm")),colour="black") + 
  	geom_text(data=biplot_df3,aes(x=text_x,y=text_y,label=Label),size=3)+
  	labs(x="CAP1 (64.02% of Constrained Variation)", y="CAP2 (18.34% of Constrained Variation)")+
	  theme_bw() +
	  theme(legend.title=element_blank(),
		legend.background = element_rect(fill = "white"),
		panel.grid.major = element_line(colour = "grey40"),
		panel.grid.minor = element_blank(),
		legend.key = element_blank()) +
  	coord_fixed() +
  	xlim(-2.0, 2.0) +
  	ylim(-2.1, 2.1)
dev.off()
```

Test for differences between intra-steer distances and intra-diet distances in the viral metagenomes. Intra-diet distances are all distances between samples from the same diet while intra-steer distances are all distances between samples from the same steer. Then use a t-test to show intra-diet distances are higher than intra-steer distances. The same is not true in the microbial communities (see beta_div_microbial.Rmd).

```{r}
dm_list <- melt(viral_bc_matrix)[melt(upper.tri(viral_bc_matrix))$value, ]
viral_map2 <- viral_map[c("ID","Animal","Diet")]

names(viral_map2)[1] <- "Var1"
dm_list2 <- merge(viral_map2, dm_list, by="Var1")
names(dm_list2)[2] <- "var1_animal"
names(dm_list2)[3] <- "var1_diet"

names(viral_map2)[1] <- "Var2"
dm_list2 <- merge(viral_map2, dm_list2, by="Var2")
names(dm_list2)[2] <- "var2_animal"
names(dm_list2)[3] <- "var2_diet"

intra_diet <- dm_list2[dm_list2$var1_diet == dm_list2$var2_diet,]
intra_animal <- dm_list2[dm_list2$var1_animal == dm_list2$var2_animal,]
intra_diet$label <- "Viral\nIntra-Diet"
intra_animal$label <- "Viral\nIntra-Steer"
intra <- rbind(intra_diet, intra_animal)

tiff("figure_3b.tiff", width = 6, height = 6, units = 'in', res = 300)
ggplot(intra, aes(x = label, y = value)) + 
    geom_boxplot() + geom_point(position = position_jitter(width = 0.15)) + 
    labs(x = "", y = "Bray-Curtis Dissimilarity\n") + guides(fill = FALSE) + 
    theme(axis.text.x = element_text(colour = "black", size=12), axis.title.y = element_text(size = 19),
        axis.ticks = element_blank())
dev.off()

t.test(intra_diet$value, intra_animal$value)
```


## Open Reading Frames

Same approach as above, just using the abundance of ORFs across samples instead of median k-mer counts.

Calculate Bray-Curtis dissimilarity and plot NMDS.

```{r, engine='bash', results='hide'}
beta_diversity.py -i viral_blast2tsv/VMG.orf_table.tab.biom -o viral_blast2tsv/VMG.orf_table_bc -m bray_curtis

nmds.py -i viral_blast2tsv/VMG.orf_table_bc/bray_curtis_VMG.orf_table.tab.txt -o viral_blast2tsv/VMG.orf_table_bc_nmds.txt
```

```{r}
viral_bc <- read.table("viral_blast2tsv/VMG.orf_table_bc/bray_curtis_VMG.orf_table.tab.txt", header=TRUE, row.names=1)
viral_bc_matrix <- as.matrix(viral_bc)
viral_bc_dist <- as.dist(viral_bc_matrix)

viral_map <- read.table("viral_mapping.txt", sep="\t", header=TRUE)
viral_map$Animal <- as.factor(viral_map$Animal)

viral_nmds <- read.table("viral_blast2tsv/VMG.orf_table_bc_nmds.txt", nrow = 15, sep = "\t", header=TRUE)
colnames(viral_nmds)[1] <- "ID"
viral_nmds_map <- merge(viral_nmds, viral_map, by = "ID")
names(viral_nmds_map)[5] <- "Steer"

shape_diet <- c("Corn" = 15, "27CDS" = 16, "55CS" = 17, "40MDGS" = 18)
shape_animal <- c("346" = 15, "259" = 16, "3244" = 17, "222" = 18, "3257" = 8)

viral_diet_nmds <- ggplot(viral_nmds_map, aes(NMDS1, NMDS2)) + geom_point(aes(color = Diet), size=2.5) +
  xlab("NMDS1") + ylab("NMDS2") + 
  guides(size = FALSE) + scale_shape_manual(name = "", values = shape_diet) + 
  labs(fill = "") +
  ggtitle("Viral - ORFs - Diet") +
  theme(legend.title=element_blank(), legend.key = element_blank())
    
viral_animal_nmds <- ggplot(viral_nmds_map, aes(NMDS1, NMDS2)) + geom_point(aes(color = Steer), size=2.5) +
  xlab("NMDS1") + ylab("NMDS2") + 
  guides(size = FALSE) + scale_shape_manual(name = "", values = shape_animal) + 
  labs(fill = "") +
  ggtitle("Viral - ORFs - Steer") +
  theme(legend.title=element_blank(), legend.key = element_blank())
    
#tiff("figures/figure_s2a_orfs_nolabel.tiff", height = 6, width = 12, units='in', res=600)
#multiplot(viral_diet_nmds, viral_animal_nmds, cols = 2)
#dev.off()
```

PERMANOVA Stats.

```{r}
adonis(viral_bc_dist ~ Diet + Animal, permutations=999, random=Animal, data=viral_map)

#Test assumptions.

anova(betadisper(viral_bc_dist,viral_map$Diet))

anova(betadisper(viral_bc_dist,viral_map$Animal))

permutest(betadisper(viral_bc_dist,viral_map$Diet))

permutest(betadisper(viral_bc_dist,viral_map$Animal))
```

adonis and dbRDA analysis to investigate the influence of environmental factors

```{r}
map2 <- viral_map[c("pH", "Protein", "NDF", "K", "Zn", "VFA", "TDN", "ADF", "RFV", "Ca", "Cu", "Fe", "P", "Mg", "Mn", "S", "Na", "Mo")]
cor(map2)

viral_tab <- fread("viral_blast2tsv/VMG.orf_table.tab.txt", header=TRUE, sep="\t")
viral_df <- as.data.frame(viral_tab)
row.names(viral_df) <- viral_df$ID
viral_df <- subset(viral_df, select=-c(ID))
viral_df_t <- t(viral_df)

viral_cap <- capscale(viral_df_t ~ TDN + Zn + K + Protein + pH + VFA, data=viral_map, dist="bray")

ordistep(viral_cap, direction="backward")

viral_cap <- capscale(viral_df_t ~ TDN + Zn + Protein, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ TDN + Protein + Zn, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Protein + Zn + TDN, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Protein + TDN + Zn, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Zn + TDN + Protein, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

viral_cap <- capscale(viral_df_t ~ Zn + Protein + TDN, data = viral_map, distance = "bray")
anova.cca(viral_cap)
anova.cca(viral_cap, by="terms")
anova.cca(viral_cap, by="axis")
RsquareAdj(viral_cap)

#save(viral_cap, file="viral_cap_orf.RData")
#load("viral_cap_orf.RData")

adonis(viral_bc_dist ~ TDN + Zn + Protein ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ TDN + Protein + Zn ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Protein + Zn + TDN ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Protein + TDN + Zn ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Zn + TDN + Protein ,  permutations=999, data=viral_map)

adonis(viral_bc_dist ~ Zn + Protein + TDN ,  permutations=999, data=viral_map)
```



