---
title: "Partial Least Squares Regression"
output:
  html_document:
    keep_md: true
---

Investigating multivariate linear relationships between log tranformed viral microbial_div clusters (with greater than 1000 reads) and dietary components. This is followed up by using univariate linear regressions to confirm the strength and direction of relationships identified by PLSR.

```{r}
library(pls)
library(QuantPsyc)
library(reshape2)
library(edgeR)
options(stringsAsFactors=FALSE)

table <- read.table("viral_beta_div/viral_pc_cluster_raw_abundance.txt", header=TRUE, comment.char="", sep='\t', row.names=1)
table <- subset(table, rowSums(table) > 750)
table_matrix <- as.matrix(table)

map <- read.table("viral_mapping.txt", sep="\t", header=TRUE, row.names=1, comment.char="")
map <- map[match(colnames(table), row.names(map)),]
map2 <- as.matrix(map[c("TDN", "Zn", "microbial_div")])


d <- DGEList(counts=table_matrix, lib.size=map$reads)
logdf <- as.data.frame(cpm(d,log=TRUE))
logdf_t <- t(logdf)

pls_df <- data.frame(y=I(logdf_t), x=I(map2))
#pls.options(parallel = 4)
pls_result <- plsr(y ~ x, data = pls_df, validation = "LOO", scale=TRUE)
capture.output(summary(pls_result, what="training"), file="plsr_result.txt")
summaryfile <- read.table("plsr_result.txt", skip=7)
summaryfile$C1_exp <- summaryfile$V2
summaryfile$C2_exp <- (summaryfile$V3 - summaryfile$V2)
summaryfile$C3_exp <- (summaryfile$V4 - summaryfile$V3)
c1_top <- summaryfile[ which(summaryfile$C1_exp > 30), ]
c2_top <- summaryfile[ which(summaryfile$C2_exp > 30), ]
c3_top <- summaryfile[ which(summaryfile$C3_exp > 30), ]
pls_top <- rbind(c1_top,c2_top,c3_top)
pls_top_list <- unique(pls_top$V1)
length(pls_top_list) #375
```

Univariate regression on KOs that have >= 30% variation explained by any component.

```{r,}
log_psl <- logdf[pls_top_list,]
log_psl_t <- t(log_psl)

res_tdn <- data.frame(id = character(0), tdn_radj=character(0), tdn_p_val=character(0), tdn_coeff=character(0), tdn_coeff_stand=character(0))
for (i in 1:ncol(log_psl_t)) {
	mlr <- lm(log_psl_t[,i] ~ TDN, data=map)
	summ <- summary(mlr)
	tdn_p_val <- summ$coefficients[8]
	tdn_radj <-  summ$adj.r.squared
	name <- colnames(log_psl_t)[i]
	tdn_coeff <- mlr$coefficients[2]
	tdn_coeff_stand <- lm.beta(mlr)[1]
	res_tdn[i, ] <- c(name, tdn_radj, tdn_p_val, tdn_coeff, tdn_coeff_stand)
}
res_tdn$tdn_p_val <- as.numeric(res_tdn$tdn_p_val)
tdn_sig <- subset(res_tdn, tdn_p_val < 0.05)
dim(tdn_sig) #145

res_zn <- data.frame(id = character(0), zn_radj=character(0), zn_p_val=character(0), zn_coeff=character(0), zn_coeff_stand=character(0))
for (i in 1:ncol(log_psl_t)) {
	mlr <- lm(log_psl_t[,i] ~ Zn, data=map)
	summ <- summary(mlr)
	zn_p_val <- summ$coefficients[8]
	zn_radj <-  summ$adj.r.squared
	name <- colnames(log_psl_t)[i]
	zn_coeff <- mlr$coefficients[2]
	zn_coeff_stand <- lm.beta(mlr)[1]
	res_zn[i, ] <- c(name, zn_radj, zn_p_val, zn_coeff, zn_coeff_stand)
}
res_zn$zn_p_val <- as.numeric(res_zn$zn_p_val)
zn_sig <- subset(res_zn, zn_p_val < 0.05)
dim(zn_sig) #15

res_microbial_div <- data.frame(id = character(0), microbial_div_radj=character(0), microbial_div_p_val=character(0), microbial_div_coeff=character(0), microbial_div_coeff_stand=character(0))
for (i in 1:ncol(log_psl_t)) {
	mlr <- lm(log_psl_t[,i] ~ microbial_div, data=map)
	summ <- summary(mlr)
	microbial_div_p_val <- summ$coefficients[8]
	microbial_div_radj <-  summ$adj.r.squared
	name <- colnames(log_psl_t)[i]
	microbial_div_coeff <- mlr$coefficients[2]
	microbial_div_coeff_stand <- lm.beta(mlr)[1]
	res_microbial_div[i, ] <- c(name, microbial_div_radj, microbial_div_p_val, microbial_div_coeff, microbial_div_coeff_stand)
}
res_microbial_div$microbial_div_p_val <- as.numeric(res_microbial_div$microbial_div_p_val)
microbial_div_sig <- subset(res_microbial_div, microbial_div_p_val < 0.05)
dim(microbial_div_sig) #84

length(intersect(tdn_sig$id, zn_sig$id))  #3
length(intersect(tdn_sig$id, microbial_div_sig$id)) #0 
length(intersect(microbial_div_sig$id, zn_sig$id)) #0

res_sig <- unique(c(tdn_sig$id, zn_sig$id, microbial_div_sig$id))
length(res_sig) #241
```

Heatmap of linear regression results.

```{r}
library(ggplot2)
library(tidyr)

res1 <- merge(res_tdn, res_zn, by="id")
final_pls_table <- merge(res1, res_microbial_div, by="id")
reg_sign <- subset(final_pls_table, tdn_p_val < 0.05 | zn_p_val < 0.05 | microbial_div_p_val < 0.05)
#241

reg_hm <- data.frame(id = character(0), TDN=numeric(0), Zn=numeric(0), microbial_div=numeric(0))
options(stringsAsFactors=FALSE)
for (i in 1:nrow(reg_sign)) {
	id <- reg_sign[i, "id"]

	tdn_p <- reg_sign[i,"tdn_p_val"]
	if (tdn_p < 0.05) {
		tdn <- reg_sign[i,"tdn_coeff_stand"]
	} else {
		tdn <- 0
	}

	zn_p <- reg_sign[i,"zn_p_val"]
	if (zn_p < 0.05) {
		zn <- reg_sign[i,"zn_coeff_stand"]
	} else {
		zn <- 0
	}
	
	microbial_div_p <- reg_sign[i,"microbial_div_p_val"]
	if (microbial_div_p < 0.05) {
		microbial_div <- reg_sign[i,"microbial_div_coeff_stand"]
	} else {
		microbial_div <- 0
	}
	
	reg_hm[i, ] <- c(id, tdn, zn, microbial_div)
}

reg_hm$TDN <- as.numeric(reg_hm$TDN)
reg_hm$Zn <- as.numeric(reg_hm$Zn)
reg_hm$microbial_div <- as.numeric(reg_hm$microbial_div)
is.num <- sapply(reg_hm, is.numeric)
reg_hm[is.num] <- lapply(reg_hm[is.num], round, 3)



reg_hm_long <- gather(reg_hm, variable, reg, TDN:microbial_div, factor_key=FALSE)
reg_hm_long$variable <- as.factor(reg_hm_long$variable)

logdf$sum <- rowSums(logdf)
logdf$id <- rownames(logdf)
logdf2 <- subset(logdf, select = c(id, sum))

reg_hm_long_sum <- merge(x = reg_hm_long, y = logdf2, by = "id", all.x = TRUE)
reg_hm_long_order <- reg_hm_long_sum[with(reg_hm_long_sum, order(-sum)), ]

colorder <- c( "TDN", "Zn", "microbial_div")
tiff("plsr_hm.tiff", res=600, compression = "lzw", width=5, height=10, units="in") 
ggplot(reg_hm_long_order, aes(x = variable, y = id)) + 
  geom_tile(aes(fill=reg),color='white') + 
  scale_fill_gradient2(midpoint = 0.0, limits=c(-1.0, 1.0)) +
  scale_x_discrete(limits=colorder,labels=c("TDN","Zinc",bquote(atop(Microbial,Diversity ~ (italic(paste("H'"))))  ))) +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks = element_blank(), panel.background=element_blank(),panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),plot.background=element_blank(),legend.title=element_blank(),    
  panel.border = element_blank(), axis.text.x=element_text(face = "bold", size = 16))
dev.off()
```