---
title: "Quality Control"
output:
  html_document:
    keep_md: true
---

# Quality Control
Description.

## Viral Metagenome - Illumina MiSeq Data

Different QC steps (minor, mostly in how we trim off adaptors and dealing with ambiguous bases/homopolymers that were dealt with by the torrent server previously) were used for the illumina viral metagenome data. Once again, there apperas to be duplication issues associated with the transposon preps presumambly, so we must be careful in dealing with them to ensure their removal. There were a few rounds of sequencing multiplexed with other samples, and hence trimming a few different files and then combining the reads.

```{r, engine='bash', results='hide'}
mkdir cutadapt_qc

cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V4_S1_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V4_S1_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V9_S2_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V9_S2_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V10_S3_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V10_S3_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V11_S4_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V11_S4_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V12_S5_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V12_S5_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V13_S6_L001_R1_001.trim.fastq.gz raw_illumina_viral_run1/V13_S6_L001_R1_001.fastq.gz

	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V4_S1_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V4_S1_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V9_S2_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V9_S2_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V10_S3_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V10_S3_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V11_S4_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V11_S4_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V12_S5_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V12_S5_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc/V13_S6_L001_R2_001.trim.fastq.gz raw_illumina_viral_run1/V13_S6_L001_R2_001.fastq.gz
```

```{r, engine='bash', results='hide'}
mkdir cutadapt_qc2
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V4_S1_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V4_S1_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V9_S2_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V9_S2_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V10_S3_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V10_S3_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V11_S4_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V11_S4_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V12_S5_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V12_S5_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V13_S6_L001_R1_001.trim.fastq.gz raw_illumina_viral_run2/V13_S6_L001_R1_001.fastq.gz

cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V4_S1_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V4_S1_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V9_S2_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V9_S2_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V10_S3_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V10_S3_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V11_S4_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V11_S4_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V12_S5_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V12_S5_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc2/V13_S6_L001_R2_001.trim.fastq.gz raw_illumina_viral_run2/V13_S6_L001_R2_001.fastq.gz
```

```{r, engine='bash', results='hide'}
mkdir cutadapt_qc3
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v9_S2_L001_R1_001.trim.fastq.gz raw_illumina_viral_run3/v9_S2_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v10_S3_L001_R1_001.trim.fastq.gz raw_illumina_viral_run3/v10_S3_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v12_S4_L001_R1_001.trim.fastq.gz raw_illumina_viral_run3/v12_S4_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v13_S5_L001_R1_001.trim.fastq.gz raw_illumina_viral_run3/v13_S5_L001_R1_001.fastq.gz

cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v9_S2_L001_R2_001.trim.fastq.gz raw_illumina_viral_run3/v9_S2_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v10_S3_L001_R2_001.trim.fastq.gz raw_illumina_viral_run3/v10_S3_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v12_S4_L001_R2_001.trim.fastq.gz raw_illumina_viral_run3/v12_S4_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc3/v13_S5_L001_R2_001.trim.fastq.gz raw_illumina_viral_run3/v13_S5_L001_R2_001.fastq.gz
```

```{r, engine='bash', results='hide'}
mkdir cutadapt_qc4
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v4_S1_L001_R1_001.trim.fastq.gz raw_illumina_viral_run4/v4_S1_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v10_S2_L001_R1_001.trim.fastq.gz raw_illumina_viral_run4/v10_S2_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v11_S3_L001_R1_001.trim.fastq.gz raw_illumina_viral_run4/v11_S3_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v12_S4_L001_R1_001.trim.fastq.gz raw_illumina_viral_run4/v12_S4_L001_R1_001.fastq.gz
	
cutadapt -n 2 -u -25 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v13_S5_L001_R1_001.trim.fastq.gz raw_illumina_viral_run4/v13_S5_L001_R1_001.fastq.gz

cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v4_S1_L001_R2_001.trim.fastq.gz raw_illumina_viral_run4/v4_S1_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v10_S2_L001_R2_001.trim.fastq.gz raw_illumina_viral_run4/v10_S2_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v11_S3_L001_R2_001.trim.fastq.gz raw_illumina_viral_run4/v11_S3_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v12_S4_L001_R2_001.trim.fastq.gz raw_illumina_viral_run4/v12_S4_L001_R2_001.fastq.gz
	
cutadapt -n 2 -u -100 -b TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTGACGCTGCCGACGA -b GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCTCCGAGCCCACGAGAC -b AGATGTGTATAAGAGACAG -b CTGTCTCTTATACACATCT -o cutadapt_qc4/v13_S5_L001_R2_001.trim.fastq.gz raw_illumina_viral_run4/v13_S5_L001_R2_001.fastq.gz
```

Remove seqeunces that have an estimated error rate >1%:

```{r, engine='bash', results='hide'}
mkdir usearch_qc
gunzip -d cutadapt_qc/*
	
usearch8.0.1623 -fastq_filter cutadapt_qc/V4_S1_L001_R1_001.trim.fastq -fastqout usearch_qc/V4_S1_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V4_S1_L001_R2_001.trim.fastq -fastqout usearch_qc/V4_S1_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V9_S2_L001_R1_001.trim.fastq -fastqout usearch_qc/V9_S2_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V9_S2_L001_R2_001.trim.fastq -fastqout usearch_qc/V9_S2_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V10_S3_L001_R1_001.trim.fastq -fastqout usearch_qc/V10_S3_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V10_S3_L001_R2_001.trim.fastq -fastqout usearch_qc/V10_S3_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V11_S4_L001_R1_001.trim.fastq -fastqout usearch_qc/V11_S4_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V11_S4_L001_R2_001.trim.fastq -fastqout usearch_qc/V11_S4_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V12_S5_L001_R1_001.trim.fastq -fastqout usearch_qc/V12_S5_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V12_S5_L001_R2_001.trim.fastq -fastqout usearch_qc/V12_S5_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V13_S6_L001_R1_001.trim.fastq -fastqout usearch_qc/V13_S6_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc/V13_S6_L001_R2_001.trim.fastq -fastqout usearch_qc/V13_S6_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

```

```{r, engine='bash', results='hide'}
mkdir usearch_qc2
gunzip -d cutadapt_qc2/*

usearch8.0.1623 -fastq_filter cutadapt_qc2/V4_S1_L001_R1_001.trim.fastq -fastqout usearch_qc2/V4_S1_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V4_S1_L001_R2_001.trim.fastq -fastqout usearch_qc2/V4_S1_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V9_S2_L001_R1_001.trim.fastq -fastqout usearch_qc2/V9_S2_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V9_S2_L001_R2_001.trim.fastq -fastqout usearch_qc2/V9_S2_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V10_S3_L001_R1_001.trim.fastq -fastqout usearch_qc2/V10_S3_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V10_S3_L001_R2_001.trim.fastq -fastqout usearch_qc2/V10_S3_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V11_S4_L001_R1_001.trim.fastq -fastqout usearch_qc2/V11_S4_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V11_S4_L001_R2_001.trim.fastq -fastqout usearch_qc2/V11_S4_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V12_S5_L001_R1_001.trim.fastq -fastqout usearch_qc2/V12_S5_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V12_S5_L001_R2_001.trim.fastq -fastqout usearch_qc2/V12_S5_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V13_S6_L001_R1_001.trim.fastq -fastqout usearch_qc2/V13_S6_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc2/V13_S6_L001_R2_001.trim.fastq -fastqout usearch_qc2/V13_S6_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80
```

```{r, engine='bash', results='hide'}
mkdir usearch_qc3
gunzip -d cutadapt_qc3/*
	
usearch8.0.1623 -fastq_filter cutadapt_qc3/v9_S2_L001_R1_001.trim.fastq -fastqout usearch_qc3/v9_S2_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v9_S2_L001_R2_001.trim.fastq -fastqout usearch_qc3/v9_S2_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v10_S3_L001_R1_001.trim.fastq -fastqout usearch_qc3/v10_S3_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v10_S3_L001_R2_001.trim.fastq -fastqout usearch_qc3/v10_S3_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v12_S4_L001_R1_001.trim.fastq -fastqout usearch_qc3/v12_S4_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v12_S4_L001_R2_001.trim.fastq -fastqout usearch_qc3/v12_S4_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v13_S5_L001_R1_001.trim.fastq -fastqout usearch_qc3/v13_S5_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc3/v13_S5_L001_R2_001.trim.fastq -fastqout usearch_qc3/v13_S5_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80
```

```{r, engine='bash'}
mkdir usearch_qc4
gunzip -d cutadapt_qc4/*

usearch8.0.1623 -fastq_filter cutadapt_qc4/v4_S1_L001_R1_001.trim.fastq -fastqout usearch_qc4/v4_S1_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v4_S1_L001_R2_001.trim.fastq -fastqout usearch_qc4/v4_S1_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v10_S2_L001_R1_001.trim.fastq -fastqout usearch_qc4/v10_S2_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v10_S2_L001_R2_001.trim.fastq -fastqout usearch_qc4/v10_S2_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v11_S3_L001_R1_001.trim.fastq -fastqout usearch_qc4/v11_S3_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v11_S3_L001_R2_001.trim.fastq -fastqout usearch_qc4/v11_S3_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v12_S4_L001_R1_001.trim.fastq -fastqout usearch_qc4/v12_S4_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v12_S4_L001_R2_001.trim.fastq -fastqout usearch_qc4/v12_S4_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v13_S5_L001_R1_001.trim.fastq -fastqout usearch_qc4/v13_S5_L001_R1_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80

usearch8.0.1623 -fastq_filter cutadapt_qc4/v13_S5_L001_R2_001.trim.fastq -fastqout usearch_qc4/v13_S5_L001_R2_001_usearch_error.fastq -fastq_maxns 1 -fastq_maxee_rate 0.01 -fastq_minlen 80
```

merge read1 and read2 together, many of reverse reads lost due to quality falling off early in V3 chemistry, not worth getting pairs back together.

```{r, engine='bash', results='hide'}
cat usearch_qc/V4_S1_L001_R1_001_usearch_error.fastq usearch_qc/V4_S1_L001_R2_001_usearch_error.fastq > usearch_qc/V4_S1_L001_R1_R2.fastq

cat usearch_qc/V9_S2_L001_R1_001_usearch_error.fastq usearch_qc/V9_S2_L001_R2_001_usearch_error.fastq > usearch_qc/V9_S2_L001_R1_R2.fastq

cat usearch_qc/V10_S3_L001_R1_001_usearch_error.fastq usearch_qc/V10_S3_L001_R2_001_usearch_error.fastq > usearch_qc/V10_S3_L001_R1_R2.fastq

cat usearch_qc/V11_S4_L001_R1_001_usearch_error.fastq usearch_qc/V11_S4_L001_R2_001_usearch_error.fastq > usearch_qc/V11_S4_L001_R1_R2.fastq

cat usearch_qc/V12_S5_L001_R1_001_usearch_error.fastq usearch_qc/V12_S5_L001_R2_001_usearch_error.fastq > usearch_qc/V12_S5_L001_R1_R2.fastq

cat usearch_qc/V13_S6_L001_R1_001_usearch_error.fastq usearch_qc/V13_S6_L001_R2_001_usearch_error.fastq > usearch_qc/V13_S6_L001_R1_R2.fastq

cat usearch_qc2/V4_S1_L001_R1_001_usearch_error.fastq usearch_qc2/V4_S1_L001_R2_001_usearch_error.fastq > usearch_qc2/V4_S1_L001_R1_R2.fastq

cat usearch_qc2/V9_S2_L001_R1_001_usearch_error.fastq usearch_qc2/V9_S2_L001_R2_001_usearch_error.fastq > usearch_qc2/V9_S2_L001_R1_R2.fastq

cat usearch_qc2/V10_S3_L001_R1_001_usearch_error.fastq usearch_qc2/V10_S3_L001_R2_001_usearch_error.fastq > usearch_qc2/V10_S3_L001_R1_R2.fastq

cat usearch_qc2/V11_S4_L001_R1_001_usearch_error.fastq usearch_qc2/V11_S4_L001_R2_001_usearch_error.fastq > usearch_qc2/V11_S4_L001_R1_R2.fastq

cat usearch_qc2/V12_S5_L001_R1_001_usearch_error.fastq usearch_qc2/V12_S5_L001_R2_001_usearch_error.fastq > usearch_qc2/V12_S5_L001_R1_R2.fastq

cat usearch_qc2/V13_S6_L001_R1_001_usearch_error.fastq usearch_qc2/V13_S6_L001_R2_001_usearch_error.fastq > usearch_qc2/V13_S6_L001_R1_R2.fastq

cat usearch_qc3/v9_S2_L001_R1_001_usearch_error.fastq usearch_qc3/v9_S2_L001_R2_001_usearch_error.fastq > usearch_qc3/v9_S2_L001_R1_R2.fastq

cat usearch_qc3/v10_S3_L001_R1_001_usearch_error.fastq usearch_qc3/v10_S3_L001_R2_001_usearch_error.fastq > usearch_qc3/v10_S3_L001_R1_R2.fastq

cat usearch_qc3/v12_S4_L001_R1_001_usearch_error.fastq usearch_qc3/v12_S4_L001_R2_001_usearch_error.fastq > usearch_qc3/v12_S4_L001_R1_R2.fastq

cat usearch_qc3/v13_S5_L001_R1_001_usearch_error.fastq usearch_qc3/v13_S5_L001_R2_001_usearch_error.fastq > usearch_qc3/v13_S5_L001_R1_R2.fastq

cat usearch_qc4/v4_S1_L001_R1_001_usearch_error.fastq usearch_qc4/v4_S1_L001_R2_001_usearch_error.fastq > usearch_qc4/v4_S1_L001_R1_R2.fastq

cat usearch_qc4/v10_S2_L001_R1_001_usearch_error.fastq usearch_qc4/v10_S2_L001_R2_001_usearch_error.fastq > usearch_qc4/v10_S2_L001_R1_R2.fastq

cat usearch_qc4/v11_S3_L001_R1_001_usearch_error.fastq usearch_qc4/v11_S3_L001_R2_001_usearch_error.fastq > usearch_qc4/v11_S3_L001_R1_R2.fastq

cat usearch_qc4/v12_S4_L001_R1_001_usearch_error.fastq usearch_qc4/v12_S4_L001_R2_001_usearch_error.fastq > usearch_qc4/v12_S4_L001_R1_R2.fastq

cat usearch_qc4/v13_S5_L001_R1_001_usearch_error.fastq usearch_qc4/v13_S5_L001_R2_001_usearch_error.fastq > usearch_qc4/v13_S5_L001_R1_R2.fastq
```

Use prinseq to remove duplicates with prefix filter of 80 bp.

```{r, engine='bash', results='hide'}
for f in usearch_qc/*_R2.fastq
do
  filename=$(basename "$f")
	filename="${filename%_*}"
	perl prinseq-lite-0.20.4/prinseq-lite.pl -trim_to_len 80 -derep 1 -fastq $f -out_format 2 -out_good usearch_qc/"$filename""_R2_truncatederep"
	grep ">" usearch_qc/"$filename""_R2_truncatederep.fasta" | cut -c 2- > usearch_qc/"$filename""_R2_keep_ids.txt"
	filter_fasta.py -f $f -s usearch_qc/"$filename""_R2_keep_ids.txt" -o usearch_qc/"$filename""_R2_finalQC.fastq"
done
	
for f in usearch_qc2/*_R2.fastq
do
	filename=$(basename "$f")
	filename="${filename%_*}"
	perl prinseq-lite-0.20.4/prinseq-lite.pl -trim_to_len 80 -derep 1 -fastq $f -out_format 2 -out_good usearch_qc2/"$filename""_R2_truncatederep"
	grep ">" usearch_qc2/"$filename""_R2_truncatederep.fasta" | cut -c 2- > usearch_qc2/"$filename""_R2_keep_ids.txt"
	filter_fasta.py -f $f -s usearch_qc2/"$filename""_R2_keep_ids.txt" -o usearch_qc2/"$filename""_R2_finalQC.fastq"
done
	
for f in usearch_qc3/*_R2.fastq
do
	filename=$(basename "$f")
	filename="${filename%_*}"
	perl prinseq-lite-0.20.4/prinseq-lite.pl -trim_to_len 80 -derep 1 -fastq $f -out_format 2 -out_good usearch_qc3/"$filename""_R2_truncatederep"
	grep ">" usearch_qc3/"$filename""_R2_truncatederep.fasta" | cut -c 2- > usearch_qc3/"$filename""_R2_keep_ids.txt"
	filter_fasta.py -f $f -s usearch_qc3/"$filename""_R2_keep_ids.txt" -o usearch_qc3/"$filename""_R2_finalQC.fastq"
done
	
for f in usearch_qc4/*_R2.fastq
do
	filename=$(basename "$f")
	filename="${filename%_*}"
	perl prinseq-lite-0.20.4/prinseq-lite.pl -trim_to_len 80 -derep 1 -fastq $f -out_format 2 -out_good usearch_qc4/"$filename""_R2_truncatederep"
	grep ">" usearch_qc4/"$filename""_R2_truncatederep.fasta" | cut -c 2- > usearch_qc4/"$filename""_R2_keep_ids.txt"
	filter_fasta.py -f $f -s usearch_qc4/"$filename""_R2_keep_ids.txt" -o usearch_qc4/"$filename""_R2_finalQC.fastq"
done
```

Combine reads from all runs together for each sample.

```{r, engine='bash'}
cat usearch_qc/V4_S1_L001_R1_R2_finalQC.fastq usearch_qc2/V4_S1_L001_R1_R2_finalQC.fastq usearch_qc4/v4_S1_L001_R1_R2_finalQC.fastq > V4.illumina.cat.fastq

cat usearch_qc/V9_S2_L001_R1_R2_finalQC.fastq usearch_qc2/V9_S2_L001_R1_R2_finalQC.fastq usearch_qc3/v9_S2_L001_R1_R2_finalQC.fastq > V9.illumina.cat.fastq

cat usearch_qc/V10_S3_L001_R1_R2_finalQC.fastq usearch_qc2/V10_S3_L001_R1_R2_finalQC.fastq usearch_qc3/v10_S3_L001_R1_R2_finalQC.fastq usearch_qc4/v10_S2_L001_R1_R2_finalQC.fastq > V10.illumina.cat.fastq

cat usearch_qc/V11_S4_L001_R1_R2_finalQC.fastq usearch_qc2/V11_S4_L001_R1_R2_finalQC.fastq usearch_qc4/v11_S3_L001_R1_R2_finalQC.fastq > V11.illumina.cat.fastq

cat usearch_qc/V12_S5_L001_R1_R2_finalQC.fastq usearch_qc2/V12_S5_L001_R1_R2_finalQC.fastq usearch_qc3/v12_S4_L001_R1_R2_finalQC.fastq usearch_qc4/v12_S4_L001_R1_R2_finalQC.fastq > V12.illumina.cat.fastq

cat usearch_qc/V13_S6_L001_R1_R2_finalQC.fastq usearch_qc2/V13_S6_L001_R1_R2_finalQC.fastq usearch_qc3/v13_S5_L001_R1_R2_finalQC.fastq usearch_qc4/v13_S5_L001_R1_R2_finalQC.fastq > V13.illumina.cat.fastq
```

Get a FASTA version.

```{r, engine='bash', results='hide'}
for f in *cat.fastq
do
  filename=$(basename "$f")
  filename="${filename%.*}"
  fastq-to-fasta.py $f -o "$filename"".fna"
done
```

Resulting read numbers.

```{r, engine='bash'}
grep -c ">" *.cat.fastq
```


## rRNA contamination - Viral Metagenome - Ion Torrent Data

Look at rRNA contamination rates. For some reason I can only get this to run from within the examples folder.  So, move all the fasta files generated to the examples folder within rRNA predictor.

```{r, engine='bash'}
mkdir rRNA_prediction/examples/e1/viral_input
mkdir rRNA_prediction/examples/e1/viral_output
cp prinseq_output/*.fna rRNA_prediction/examples/e1/viral_input/

cd rRNA_prediction/examples/e1
export PATH=//work/samodha/canderson3/rRNA_prediction/rRNA_hmm_fs_wst_v0:$PATH
/work/samodha/canderson3/rRNA_prediction/scripts/rRNA_hmm_run_wst_v0.pl  viral_input viral_output
cd ../../..
```

Check the number of rRNA hits for each sample using custom script to parse outputs:

```{r, engine='bash'}
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.1_trimm_finalQC.fna.coord scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.2_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.3_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.4_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.5_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.6_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.7_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.8_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.9_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.10_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.11_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.12_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.13_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.14_trimm_finalQC.fna.coord
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_output/VMG.15_trimm_finalQC.fna.coord ```
```

## rRNA contamination - Viral Metagenome - Illumina MiSeq Data

Same procedure, just focusing on reads from the MiSeq data.

```{r, engine='bash'}
cp *.illumina.cat.fna rRNA_prediction/examples/e1/viral_illumina_input/
cd rRNA_prediction/examples/e1
export PATH=//work/samodha/canderson3/rRNA_prediction/rRNA_hmm_fs_wst_v0:$PATH
/work/samodha/canderson3/rRNA_prediction/scripts/rRNA_hmm_run_wst_v0.pl  viral_illumina_input viral_illumina_output
cd ../../..
```

Check the results.

```{r, engine='bash'}
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V4.illumina.cat.fna.coord 
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V9.illumina.cat.fna.coord 
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V10.illumina.cat.fna.coord 
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V11.illumina.cat.fna.coord 
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V12.illumina.cat.fna.coord 
scripts/./parse_rRNA_output.pl -rrna rRNA_prediction/examples/e1/viral_illumina_output/V13.illumina.cat.fna.coord 
```
